Solving Horn clauses over LI

### 2012-12-19 article.tex

\usepackage{fullpage,url}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{syntax}

\title{How to make a delicious pizza}
\author{Yuto Takei}
\institute{The University of Tokyo}

\begin{document}

\maketitle

\begin{abstract}
  This is the abstract.
\end{abstract}

@@

Definition of Horn clause solving (Informal)

Advantages
* Solution space consideration

Discussion on Real space

\section{Algorithm Overview}

@@

\setlength{\grammarparsep}{-2pt}
\setlength{\grammarindent}{6em}
\begin{grammar}

<num> ::= All integers

<var> ::= Arithmetic variables

<term> ::= $<num> \cdot <var>$

<expr> ::=  $<term> + <term> + \cdots + <num> \leq 0$

<la> ::= $<expr>$ | $<la> \wedge <la>$

<pvar> ::= Predicate variables

<pred> ::= $<pvar> ( <var>, <var>, ... )$

<hTerm> ::= <la> | <pred>

<horn> ::= $<hTerm> \wedge <hTerm> \wedge \cdots \longrightarrow <hTerm>$

@@

* We consider inequalities.
** NOTE: Even we have =, <>, >, <=, we can normalize to >=
         over integer space

@@

Def <Resolution Tree>:

@@

>>>>

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{syntax}

\title{Solving Horn clauses over LI}
\author{Yuto Takei}
\institute{The University of Tokyo}

\begin{document}
\maketitle
\begin{abstract}
  This is the abstract.
\end{abstract}

@@

Horn clause solving is a problem of constraint solving that is consisted of multiple Horn clauses with unknown predicate symbols. The solution is an assignment for such symbols so that all given Horn clauses stay valid. There may be multiple solutions for one problem, and the algorithm is expected to show at least one.

In this paper, we present a novel algorithm to solve Horn clauses. As the unique feature of the algorithm, we preserve the solution space throughout the computation. We are able to provide multiple assignments for predicate symbols. Additionally, this technique enables us to handle general Horn clauses rather than the recursion-free ones, which was the major restriction of the previous work.

The rest of our paper is structured as follows: Section 2 shows the basic algorithm to solve recursion-free Horn clauses with solution space consideration. Section 3 extends this algorithm so that it works on general settings. Section 4 discusses the complexity and the completeness of the extended algorithm. Section 5 illustrates the experimental result. Finally Section 6 brings the conclusion.

\section{Algorithm}

@@

\setlength{\grammarindent}{6em}
\begin{grammar}

<t> ::= $n$ | $nv$ | $t + t$

<e> ::= $t \leq 0$ | $e \wedge e$

<p> ::= $P (v, v, ... )$

<x> ::= $e$ | $p$

<h> ::= $x \wedge x \wedge \cdots \longrightarrow x$

@@

* We consider inequalities.
** NOTE: Even we have =, $\neq$, >, <=, we can normalize to >=
         over integer space

@@

Def <Implication Tree>:

@@

?
